\item[{\color{numcolor}\scriptsize19}] 2021: The Milky Way is not special: accreted stars also inhabit the Spite Plateau, at \textit{ASA Annual Scientific Meeting}. Melbourne, Australia.
\item[{\color{numcolor}\scriptsize18}] 2021: The Milky Way is not special: accreted stars also inhabit the Spite Plateau, at \textit{GALAH Science Meeting}. Sydney, Australia.
\item[{\color{numcolor}\scriptsize17}] 2019: The Galah Survey: Chemically tagging the Fimbulthul stream to the globular cluster $\omega$ Centauri, at \textit{Gaia-ESO Science Meeting}. Florence, Italy.
\item[{\color{numcolor}\scriptsize16}] 2019: (Poster) The Fimbulthul stellar stream was tidally stripped from the globular cluster $\omega$ Centauri, at \textit{ASA Annual Scientific Meeting}. Brisbane, Australia. (Winner of Best Poster)
\item[{\color{numcolor}\scriptsize15}] 2019: Mapping stellar streams with LSST, at \textit{LSST@Asia}. Sydney, Australia.
\item[{\color{numcolor}\scriptsize14}] 2018: A very nitrogen-rich star in the very low-mass, very metal-poor cluster ESO280-SC06, at \textit{Survival of Dense Star Clusters in the Milky Way System}. Heidelberg, Germany.
\item[{\color{numcolor}\scriptsize13}] 2018: Flying the nest to the Magellanic Clouds and Bridge with GALAH and TESS-HERMES~, at \textit{ASA Annual Scientific Meeting}. Melbourne, Australia.
\item[{\color{numcolor}\scriptsize12}] 2018: Pushing the envelope on globular clusters, at  \textit{ASA Annual Scientific Meeting}. Melbourne, Australia.
\item[{\color{numcolor}\scriptsize11}] 2017: The GALAH survey: Discovery of dissolving star clusters, at  \textit{Surveying the Cosmos, The Science From Massively Multiplexed Surveys}. Sydney, Australia.
\item[{\color{numcolor}\scriptsize10}] 2017: What happened to the horizontal branch of ESO280-SC06? at \textit{Stars in Sydney}. Sydney, Australia.
\item[{\color{numcolor}\scriptsize9}] 2017: The GALAH survey: Co-orbiting stars and chemical tagging, at  \textit{Celebration of CEMP \& Gala of GALAH workshop}. Melbourne, Australia.
\item[{\color{numcolor}\scriptsize8}] 2017: What happened to the horizontal branch of ESO280-SC06? at \textit{Australian Institute of Physics Summer Meeting 2017}. Sydney, Australia.
\item[{\color{numcolor}\scriptsize7}] 2016: Probing the low-mass regime of globular clusters, at  \textit{Multiple populations in globular clusters: Where do we stand?} Sexten, Italy.
\item[{\color{numcolor}\scriptsize6}] 2016: Tips and tools to work with reduced data, at  \textit{ITSO/AAO Observational Techniques Workshop}. Sydney, Australia.
\item[{\color{numcolor}\scriptsize5}] 2015: Searching extra-tidal stars of globular clusters with the GALAH survey, at  \textit{Multiwavelength Dissection of Galaxies}. Sydney, Australia.
\item[{\color{numcolor}\scriptsize4}] 2014: C+N+O abundance of evolved stars of NGC1851, at  \textit{Bolton Symposium}. Sydney, Australia.
\item[{\color{numcolor}\scriptsize3}] 2013: Spectral matching for elemental abundances of evolved stars of globular clusters, at \textit{The Origin of Cosmic Elements}. Barcelona, Spain.
\item[{\color{numcolor}\scriptsize2}] 2012: Carbon, nitrogen and barium abundances of giant branch stars of $\omega$ Centauri using spectral matching, at \textit{Nuclei in the Cosmos}. Cairns, Australia.
\item[{\color{numcolor}\scriptsize1}] 2011: Stellar parameters and barium abundances in $\omega$ Centauri GB by spectral matching, at  \textit{6th Stromlo Symposium on IFU Science in Australia}. Canberra, Australia.
